---
title: "American Nyckelharpa Association 2021 Survey Analysis"
author: "Genelle Denzin"
output: 
  html_document:
    theme: cerulean
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# for reproducibility, please create a data directory containing both the member and general survey files in your project

library(tidyverse)
library(lubridate)
library(ggplot2)
library(janitor)
library(tidytext)
library(here)
library(viridis)
library(scales)
library(gt)
library(english)

source(here("survey.R"))

member_responses <- member %>% nrow()
general_responses <- general %>% nrow()

```

# Survey Summary 

<font size = "4">Hi if you participated in this survey, you will be interested to see some results. We are excited to share with you some interesting insights!

  * Member survey: `r member_responses` respondents 
  * General survey: `r general_responses` respondents
  * **Total: `r member_responses + general_responses` total responses**

## Instrument Types 

```{r interests}
interests <- rbind(
  general %>%
    select(
      Experience,
      StyleAndType,
      Faves,
      InterestInSwedish,
      InterestInUppland,
      SurveyType
    ),
  member %>%
    select(
      Experience,
      StyleAndType,
      Faves,
      InterestInSwedish,
      InterestInUppland,
      SurveyType
    )
) %>% unique()


instrument_type <- interests %>%
  mutate(
    Type = case_when(
      str_detect(tolower(StyleAndType), "row or 4") == TRUE ~ "Not specified",
      (str_detect(tolower(StyleAndType), "3") |
        str_detect(tolower(StyleAndType), "three")) &
        str_detect(tolower(StyleAndType), "4") == TRUE ~ "Both or Multiple",
      str_detect(tolower(StyleAndType), "3 row") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "3-row") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "3row") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "three") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "4 row") == TRUE ~ "4 row",
      str_detect(tolower(StyleAndType), "4-row") == TRUE ~ "4 row",
      TRUE ~ "Not specified"
    )
  ) %>%
  filter(Type != "Not specified") %>%
  count(SurveyType, Type)
```

A total of `r instrument_type %>% filter(Type == "3 row") %>% summarise(t = sum(n)) %>% pull(t)`, or `r percent(instrument_type %>% filter(Type == "3 row") %>% summarise(t = sum(n)) %>% pull(t)/ instrument_type %>% summarise(t = sum(n)) %>% pull(t))` of respondents are working with a 3-row nyckelharpa, and we did find a difference in ANA members and non-members, with more members having 4-row and multiple types of harpas than respondents who were not members.

```{r instrument_plot}
ggplot(instrument_type, aes(y = n, x = SurveyType)) +
  geom_bar(position = "fill", stat = "identity", 
           aes(fill = Type)) +
  scale_fill_viridis(discrete = TRUE, alpha = .8) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "Survey Type", y = "") +
  scale_y_continuous(labels = scales::percent)


```

## Experience

blah blah

```{r}
experience <- rbind(general %>%
                      select(Experience, SurveyType),
                    member %>% select(Experience, SurveyType)) %>%
  mutate(
    ExperienceAdjust = case_when(
      str_detect(Experience, "5 years,") |
        str_detect(Experience, "15") |
        str_detect(Experience, "Leif") ~ "More than 5 years",
      str_detect(Experience, "Never") |
        str_detect(Experience, "awhile") |
        str_detect(Experience, "priority") ~ "I don't play (yet)",
      str_detect(Experience, "4 years") ~ "2-5 years",
      TRUE ~ Experience
    ),
    ExperienceAdjust = factor(ExperienceAdjust,
                              levels = c(
                                "I don't play (yet)",
                                "0-2 years",
                                "2-5 years",
                                "More than 5 years"
                              ))
  )

experience %>%
  count(ExperienceAdjust, SurveyType) %>%
  ggplot(aes(x = SurveyType, y = n, fill = ExperienceAdjust)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis("", discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "Survey Type", y = "", title = "Experience") 
```


## Styles

Top 5 most used words of interest in regard to style of playing across both the member and general surveys.

```{r styles}

styles <- interests %>%
  select(StyleAndType) %>%
  mutate(StyleAndType = str_replace(StyleAndType, "/", " ")) %>%
  separate(
    StyleAndType,
    into = c(letters, LETTERS, 
             paste0(letters, "a"), 
             paste0(LETTERS, "a")),
    fill = "right",
    sep = " "
  ) %>%
  pivot_longer(cols = everything(),
               names_to = "deletethis") %>%
  select(-deletethis) %>%
  mutate(
    value = tolower(value),
    value = str_replace_all(tolower(value), "traditional", "trad"),
    value = str_replace_all(value, "trad", "traditional"),
    value = gsub("[[:punct:][:blank:]]+", " ", value),
    value = str_trim(value, side = "both"),
    CharLength = nchar(value)
  ) %>%
  filter(CharLength > 3 &
           str_detect(value, "3") == FALSE &
           str_detect(value, "4") == FALSE &
           !value %in% c("also", "mostly", "tuned", "like", "from",
                         "play", "music", "tunes", "tuning",
                         "nyckelharpa", "repertoire", "chromatic",
                         "standard", "fiddle")) %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(5) %>%
  rename("Word" = value, "Frequency" = n) %>%
  mutate(Word = str_to_title(Word))

style_count <- interests %>%
  select(StyleAndType) %>%
  filter(!is.na(StyleAndType)) %>%
  nrow()

styles %>%
  mutate(Word = fct_reorder(Word, desc(Frequency))) %>%
  ggplot(aes(x = Word, y = Frequency, fill = Word)) +
  geom_col() +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Styles",
    caption = paste(style_count,
                     "respondents used these words most often"),
    x = "",
    y = ""
  ) +
  geom_hline(aes(yintercept = style_count + 2)) +
  scale_fill_viridis(discrete = TRUE) +
  geom_label(
    label = paste(style_count, "respondents"),
    x = 4.1,
    y = style_count + 1,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  theme(axis.text.x = 
          element_text(angle = 33, vjust = 0.5, hjust=1)) + 
  guides(fill = "none") 

```

### Favorite Tunes

```{r}

too_many <- interests %>%
  select(Faves) %>%
  mutate(
    TooMany =
      case_when(
        Faves == "N/A" | is.na(Faves) ~ "No response",
        str_detect(tolower(Faves),
                   "too many",
                   negate = TRUE) == FALSE &
          str_detect(Faves, "That is a very hard question",
                     negate = FALSE) == FALSE ~ "TRUE",
        TRUE ~ "FALSE"
      )
  ) %>%
  count(TooMany)

```

Of the `r too_many %>% filter(TooMany == "FALSE") %>% pull(n) + too_many %>% filter(TooMany == "TRUE") %>% pull(n)` who answered the question about their 3 favorite tunes, `r too_many %>% filter(TooMany == "TRUE") %>% pull(n)` protested that the question was too difficult given how many great tunes there are. Of those who included tune names in their response, here are some tunes named more than once.

```{r}

tunes <- interests %>%
  select(Faves) %>%
  mutate(
    TooMany =
      case_when(
        Faves == "N/A" | is.na(Faves) ~ "No response",
        str_detect(tolower(Faves),
                   "too many",
                   negate = TRUE) == FALSE &
          str_detect(Faves, "That is a very hard question",
                     negate = FALSE) == FALSE ~ "TRUE",
        TRUE ~ "FALSE"
      ),
    Faves = str_replace_all(Faves, ";", ","),
    Faves = str_replace(tolower(Faves), "currently ", ""),
    Faves = str_replace_all(tolower(Faves),
                            "spelmansgladje",
                            "spelmansglädje"),
    Faves = case_when(
      Faves ==
        "zakaria jansons polska / gånglåt från laggars / polska efter andersson" ~
        "zakaria jansons polska, gånglåt från laggars, polska efter andersson",
      str_detect(tolower(Faves), "i suppose something") ~
        "ipa gubban, josefine's waltz",
      tolower(Faves) == "båtsman däck  -boda waltz   timeless waltz" ~
        "båtsman däck, boda waltz, timeless waltz",
      str_starts(tolower(Faves), "stures") ~
        "stures schottis, halleforsnaspolska",
      TRUE ~ Faves
    ), 
    Faves = str_replace(tolower(Faves),
                        "that is a very hard question. ", "")
  ) %>%
  filter(TooMany == "FALSE") %>%
  select(-TooMany) %>%
  separate(Faves,
           into = c(letters),
           sep = ", ",
           fill = "right") %>%
  pivot_longer(cols = everything()) %>%
  filter(!is.na(value)) %>%
  mutate(
    value = str_trim(value),
    value = tolower(value),
    value = str_remove_all(value, "and "),
    value = str_remove_all(value, "also "),
    value = case_when(
      str_starts(value, "at the moment") ~ "spelmansglädje",
      value == "bygnan" ~ "byggnan",
      str_starts(value, "hard to narrow") |
        value == "harjedals schottis" ~ "härjedalsschottis",
      str_starts(value, "hom") ~ "hommage till en spelman",
      str_starts(value, "jose") |
        str_starts(value, "tough") ~ "josephine's dopvals",
      str_starts(value, "karol") ~ "karolinersmarch",
      str_starts(value, "most any tune") ~ "eklundspolska #3",
      str_starts(value, "sheesh") ~ "spelmansglädje",
      str_starts(value, "so i'll") ~ "trollrikepolskan",
      str_starts(value, "spelglädjen") ~ "spelmansglädje",
      str_starts(tolower(value), "spelmans") ~ "spelmansglädje",
      str_detect(tolower(value), "ali’s waltz") ~ "ali's waltz",
      str_starts(value, "vendelpolskan") ~ "vendelpolskan",
      TRUE ~ value
    )
  ) %>% 
  filter(str_detect(value, "lots of others", negate = TRUE),
         str_detect(value, "american question", negate = TRUE),
         str_detect(value, "but i really", negate = TRUE),
         str_detect(value, "dalarna the adjoining areas", negate = TRUE),
         str_detect(value, "i could not possibly", negate = TRUE),
         str_starts(value, "many sahlstrom", negate = TRUE),
         str_starts(value, "not sure", negate = TRUE),
         value != "oh",
         str_starts(value, "really liked", negate = TRUE),
         str_starts(value, "since that", negate = TRUE),
         str_starts(value, "so not possible", negate = TRUE),
         str_starts(value, "these vary", negate = TRUE),
         str_starts(value, "this is", negate = TRUE),
         str_detect(value, "pretty exclusively", negate = TRUE),
         str_starts(value, "too diff", negate = TRUE),
         str_starts(value, "tunes", negate = TRUE),
         str_starts(value, "wow", negate = TRUE),
         str_starts(value, "varies", negate = TRUE)
         ) %>%
  count("Tune" = value) %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>%
  mutate(Tune = str_to_title(Tune)) %>%
  rename("Mentions" = n)

gt(tunes) %>%
  tab_options(table.font.size = px(22))
	
```

### Interest in Swedish and Uppland

On a scale from 0 to 2, the average interest levels in the two traditions represented in the survey are:
```{r}

average_interest_swedish <- 
  mean(c(interests$InterestInSwedish), na.rm = TRUE) 
  
average_interest_uppland <- 
  mean(c(interests$InterestInUppland), na.rm = TRUE)

interest_national <- data.frame(Type = c("Swedish", "Uppland"),
                            AverageInterest = c(
                              average_interest_swedish,
                              average_interest_uppland
                            ),
                            Denominator = 2)

interest_national %>%
  ggplot(aes(x = Type, fill = Type)) +
  geom_segment(aes(xend = Type, y = 0, yend = AverageInterest),
               color = "dark gray") +
  geom_point(aes(y = AverageInterest),
             fill = "blue",
             size = 4, 
             alpha = .7,
             shape = 21) +
  geom_hline(yintercept = 2) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Interest in Swedish and Uppland Styles",
    x = "",
    y = "Average Interest"
  ) +
  geom_label(
    label = "Strong Interest ->",
    x = 2.5,
    y = 1.75,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
    geom_label(
    label = "<- No Interest",
    x = 2.5,
    y = .2,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() +
  guides(fill = "none")


```


## Website Feedback

### Traffic

```{r}

website <- rbind(
  general %>%
    select(SiteVisits,
           SitePurpose,
           SiteSuggestions,
           SurveyType),
  member %>%
    select(SiteVisits,
           SitePurpose,
           SiteSuggestions,
           SurveyType)
) %>% 
  unique()

how_often <- website %>%
  group_by(SurveyType) %>%
  summarise(VisitAvg = mean(SiteVisits, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Denominator = 2)

how_often %>%
  ggplot(aes(x = SurveyType, fill = SurveyType)) +
  geom_segment(aes(xend = SurveyType, y = 0, yend = VisitAvg),
               color = "dark gray") +
  geom_point(aes(y = VisitAvg),
             fill = "blue",
             size = 4, 
             alpha = .7,
             shape = 21) +
  geom_hline(yintercept = 2) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Website Visits",
    x = "",
    y = "How Often"
  ) +
  geom_label(
    label = "Often ->",
    x = 2.5,
    y = 1.85,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
    geom_label(
    label = "<- Never",
    x = 2.5,
    y = .15,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() +
  guides(fill = "none")

```

On a scale from 0 (never) to 2 (often), the average responses to how often the respondents visit the website was:

  * Non-members: **`r how_often %>% filter(SurveyType == "General") %>% pull(VisitAvg)`**
  * Members: **`r how_often %>% filter(SurveyType == "Member") %>% pull(VisitAvg)`**

### Why do people come to the website? 

There was no significant difference between responses from members vs non-members, except fewer members are looking to buy a nyckelharpa. Taking all the answers together, including respondents selecting multiple selections, here are the reasons people are coming to the website:
<br>
<br>
```{r}
site_purpose <- website %>%
  select(SitePurpose) %>%
  separate(
    SitePurpose,
    sep = ", ",
    into = c("a", "b", "c", "d", "e", "f", "g", "h"),
    fill = "right"
  ) %>%
  pivot_longer(cols = all_of(1:8)) %>%
  filter(!is.na(value)) %>%
  count(value) %>%
  filter(n > 1) %>%
  arrange(desc(n)) %>%
  rename("Reasons" = value, "Clicks" = n) %>%
  mutate(Reasons = case_when(
    str_detect(Reasons, "events") ~ "Nyckelharpa events",
    str_detect(Reasons, "maintenance") ~ "Nyckelharpa maintenance",
    str_detect(Reasons, "music") ~ "Nyckelharpa music",
    str_detect(Reasons, "instrument") ~ "Nyckelharpa & its history",
    str_detect(Reasons, "buy") ~ "How to buy a nyckelharpa"
  ))

site_purpose_count <- website %>%
  select(SitePurpose) %>%
  filter(!is.na(SitePurpose)) %>%
  nrow()

site_purpose %>%
  mutate(Reasons = fct_reorder(Reasons, Clicks)) %>%
  ggplot(aes(x = Reasons, y = Clicks, fill = Reasons)) +
  geom_col() +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Site Purpose",
    caption = 
      paste(site_purpose_count,
            "respondents selected the reasons they come to the site"), 
    x = "",
    y = ""
  ) +
  ylim(0, 75) +
  geom_hline(aes(yintercept = site_purpose_count)) +
  scale_fill_viridis(discrete = TRUE) +
  geom_label(
    label = paste(site_purpose_count, "respondents"),
    x = 4.1,
    y = site_purpose_count,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() + 
  guides(fill = "none")

```
<br>
In the space for additional comments, several respondents mentioned that they used to visit the website many years ago but not much recently. Other respondents mentioned that they come to the website for the member directory, to find nyckelharpa players in their area. **We no longer publish a player directory, but people can write to [info@nyckelharpa.org](mailto:info@nyckelharpa.org) to ask about players in their area!**

<br>

## Virtual Jam Feedback

```{r}

jams <- rbind(
  general %>%
    select(VirtualJamInterest,
           VirtualJamInterest,
           SecondSaturday,
           JamFacilitatorInterest,
           Nov13JamFeedback,
           SurveyType),
  member %>%
    select(VirtualJamInterest,
           VirtualJamInterest,
           SecondSaturday,
           JamFacilitatorInterest,
           Nov13JamFeedback,
           SurveyType)
) 

jam_interest_respondents <- 
  jams %>% 
  filter(!is.na(JamFacilitatorInterest)) %>% 
  nrow()

jam_interest <- mean(c(jams$VirtualJamInterest), na.rm = TRUE)

jam_interest_by_member_type <- 
  jams %>% 
  count(SurveyType, VirtualJamInterest)

jam_facilitator_definitely <-
  jams %>% 
  count(JamFacilitatorInterest) %>% 
  filter(JamFacilitatorInterest == 2) %>% 
  pull(n)

jam_facilitator_maybe <- 
  jams %>% 
  count(JamFacilitatorInterest) %>% 
  filter(JamFacilitatorInterest == 1) %>% 
  pull(n)

```
Of the `r jam_interest_respondents` who responded to the question gauging interest in a virtual Zoom jam, where 0 is no interest and 2 is a strong interest, the average answer was `r jam_interest`.

Comparing interest between members and non-members, most members had a strong interest, whereas non-members were more divided, but most were at least somewhat interested in a virtual jam.

Encouragingly, there was `r jam_facilitator_definitely` respondent very interested in facilitating, and `r jam_facilitator_maybe` respondents somewhat interested in facilitating a jam.

The ANA appreciates all the feedback regarding the current time slot for virtual jams and for the feedback regarding the Zoom jam held November 13, 2021. We commit to announcing upcoming virtual jams and working with volunteer facilitators. Please send feedback any time to [nyckelnotes@nyckelharpa.org](mailto:nyckelnotes@nyckelharpa.org). 

## Allspel Suggestions

```{r}

allspiel <- rbind(
  general %>%
    select(AllspielSuggestions,
           SurveyType),
  member %>%
    select(AllspielSuggestions,
           SurveyType)
) 

allspiel_responses <- allspiel %>% filter(!is.na(AllspielSuggestions))

allspiel_respondents <- 
  allspiel_responses  %>% nrow()

```

From `r allspiel_respondents` responses to the survey question asking for tune suggestions to add to the [Allspel list](http://www.nyckelharpa.org/archive/written-music/american-allspel-list/), the following tunes were noted:

  * 1814
  * Adventspolskan
  * Bisonpolska
  * Eklundapolska 1 & 3
  * Elins Vals
  * Femtolen
  * Flickorna Svensson
  * Hambo efter Carl Johan Krej
  * Hommage til en Spelman
  * Härjedalsschottis
  * Juringius
  * Karl XII Vals
  * Kyrkpolska
  * Langdans fran Solleron
  * Polska efter Hugo Falk
  * Ridmarsch efter Byss-Calle
  * Schottis fr. Härjedalen
  * Spelmansglädje
  * Stures 80-år schottis
  * Älvdalensbrudmarsch
  * Äppelbo Gånglåt
  * Österbypolska

The ANA will review this list and make revisions as necessary.  

## Virtual Workshop Feedback

```{r}
workshop <- rbind(
  general %>%
    select(starts_with("VirtualWorkshop"),
           SurveyType),
  member %>%
    select(starts_with("VirtualWorkshop"),
           SurveyType)
)

workshop_interest <- mean(c(workshop$VirtualWorkshopInterest), na.rm = TRUE)
```

### Overall Interest

Overall interest in a virtual workshop (however that is defined) on a scale from 0 (no interest) to 2 (strong interest), was an average of `r format(workshop_interest, digits = 3)`.

### Workshop Types

```{r}

tunes <- "Learning tunes"
tune_types <- "particular tune types"
dancing <- "Playing for dancing"
maintenance <- "Maintenance for your nyckelharpa"
beginners <- "Getting started with the nyckelharpa for beginners"
harmonies <- "Playing harmonies"

workshop_types <- workshop %>%
  select(VirtualWorkshopTypes) %>%
  filter(!is.na(VirtualWorkshopTypes)) %>%
  mutate(
    Tunes = if_else(str_detect(VirtualWorkshopTypes, tunes), 1, 0),
    TuneTypes = if_else(str_detect(VirtualWorkshopTypes, tune_types), 1, 0),
    Dancing = if_else(str_detect(VirtualWorkshopTypes, dancing), 1, 0),
    Maintenance = if_else(str_detect(VirtualWorkshopTypes, maintenance), 1, 0),
    Beginners = if_else(str_detect(VirtualWorkshopTypes, beginners), 1, 0),
    Harmonies = if_else(str_detect(VirtualWorkshopTypes, harmonies), 1, 0),
    Other = case_when(
      str_detect(VirtualWorkshopTypes, tunes, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, harmonies, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, tune_types, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, dancing, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, maintenance, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, beginners, negate = TRUE) ~ 
        VirtualWorkshopTypes
    )
  ) %>%
  select(-VirtualWorkshopTypes, -Other) %>%
  map_dbl(., sum) %>%
  bind_rows() %>%
  pivot_longer(cols = everything(),
               names_to = "Topics") %>%
  arrange(desc(value))

workshop_type_count <- workshop %>%
  select(VirtualWorkshopTypes) %>%
  filter(!is.na(VirtualWorkshopTypes)) %>%
  nrow()

workshop_types %>%
  mutate(Topics = fct_reorder(Topics, desc(value))) %>%
  ggplot(aes(x = Topics, y = value, fill = Topics)) +
  geom_col() +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Workshop Interest",
    caption = paste(workshop_type_count,
                     "respondents selected multiple topics"),
    x = "",
    y = ""
  ) +
  geom_hline(aes(yintercept = workshop_type_count + 2)) +
  scale_fill_viridis(discrete = TRUE) +
  geom_label(
    label = paste(workshop_type_count, "respondents"),
    x = 4.1,
    y = workshop_type_count + 1,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) + 
  coord_flip() +
  guides(fill = "none")

```
<br>

## Newsletter Feedback

```{r}

newsletter <- rbind(
  general %>%
    select(starts_with("Newsletter"),
           SurveyType),
  member %>%
    select(starts_with("Newsletter"),
           SurveyType)
)
newsletter_interest_count <- newsletter %>%
  filter(!is.na(NewsletterInterest)) %>% nrow()

newsletter_contributor_count <- newsletter %>%
  filter(!is.na(NewsletterContributorInterest)) %>% nrow()

```
Newsletter Feedback

There were `r newsletter_interest_count` respondents who indicated whether they were interested in reading an ANA newsletter, and `r newsletter_contributor_count` who indicated an interest in contributing to the creation of a newsletter.

An overview of the newsletter feedback brought out some interest, but many had concerns that it might become burdensome to create and distribute. However, it was encouraging that there were some who were interested in contributing content, layout and design services, and money toward its creation.

## Membership Feedback

### Membership Interest (from non-members)

```{r}

membership <- rbind(
  general %>%
    select(starts_with("Membership"),
           VolunteerInterest,
           SurveyType),
  member %>%
    select(starts_with("Membership"),
           VolunteerInterest,
           SurveyType) %>%
    mutate(MembershipInterest = "Already a member")
)

membership_interest_count <- membership %>%
  filter(!is.na(MembershipInterest) &
           MembershipInterest != "Already a member") %>% nrow()

membership_benefits_count <- membership %>%
  filter(!is.na(MembershipBenefits)) %>% nrow()

volunteer_interest_count <- membership %>%
  filter(!is.na(VolunteerInterest)) %>% nrow()

membership_interest <- membership %>%
  filter(!is.na(MembershipInterest) & 
           MembershipInterest != "Already a member") %>%
  mutate(
    MembershipInterest = case_when(
      MembershipInterest %in% c("Yes", "Just signed up.") ~ "Yes",
      MembershipInterest == "No" ~ "No",
      TRUE ~ "Maybe"
    ),
    MembershipInterest = factor(MembershipInterest,
                                levels = c("Yes", "Maybe", "No"))
  ) %>% 
  count(MembershipInterest) 

```

Of the `r membership_interest_count` non-member respondents who answered this question, there was strong interest in ANA membership:

```{r}

ggplot(membership_interest, 
       aes(x = MembershipInterest, y = n, fill = MembershipInterest)) +
  geom_col() +
  scale_fill_viridis(discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  guides(fill = "none") +
  labs(
    title = "Interest in Membership (from non-members)",
    x = "",
    y = ""
  )

```

### Membership Benefits

```{r}
benefits <- tribble(
  ~Benefits, ~Count,
  "discounts",	4,
  "finding others",	6,
  "access",	7,
  "na",	11,
  "none",	19
)
```

The question about membership benefits was interpreted broadly by the respondents who answered it. Here are some key takeaways:

  * Most felt like adding benefits to ANA membership was unnecessary
  * ANA membership was associated with finding other players, access to content, information about events, and a few mentioned discounts
  * Community and keeping the nyckelharpa as an instrument alive was an underlying theme

## Survey Feedback

```{r}
survey_feedback <- rbind(
  general %>%
    select(SurveyFeedback,
           SurveyType),
  member %>%
    select(SurveyFeedback,
           SurveyType)
)

survey_feedback_count <- survey_feedback %>%
  filter(!is.na(SurveyFeedback)) %>% nrow()

```

`r str_to_sentence(as.english(survey_feedback_count))` respondents gave feedback on the survey itself, though the data analyst has some to add! The ANA appreciates all the wonderful feedback about the website given in the survey. More generally, your ideas and offers to volunteer have been noted. We will be posting a list of volunteer roles that are available soon, so keep a look out. If you would like to reach out to us, please email  [nyckelnotes@nyckelharpa.org](mailto:nyckelnotes@nyckelharpa.org).

So much thanks to everyone who participated and read all the way to the last of the analysis! Hope you enjoyed reading the results! <3


