---
title: "American Nyckelharpa Association 2021 Survey Analysis"
author: "Analysis by Genelle Denzin (volunteer) and Lane Foster Harrell"
output: 
  html_document:
    theme: paper
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# for reproducibility, please create a data directory containing both the member and general survey files in your project

library(tidyverse)
library(lubridate)
library(ggplot2)
library(janitor)
library(tidytext)
library(here)
library(viridis)
library(scales)
library(gt)
library(english)

source(here("survey.R"))

member_responses <- member %>% nrow()
general_responses <- general %>% nrow()

```

# Survey Summary {.tabset}

<font size = "4">Hi if you participated in this survey, you will be interested to see some results. We are excited to share with you some interesting insights!

  * Member survey: `r member_responses` respondents 
  * General survey: `r general_responses` respondents
  * **Total: `r member_responses + general_responses` total responses**

## Instruments 

```{r interests}
interests <- rbind(
  general %>%
    select(
      Experience,
      StyleAndType,
      Faves,
      InterestInSwedish,
      InterestInUppland,
      SurveyType
    ),
  member %>%
    select(
      Experience,
      StyleAndType,
      Faves,
      InterestInSwedish,
      InterestInUppland,
      SurveyType
    )
) %>% unique()


instrument_type <- interests %>%
  mutate(
    Type = case_when(
      str_detect(tolower(StyleAndType), "row or 4") == TRUE ~ "Not specified",
      (str_detect(tolower(StyleAndType), "3") |
        str_detect(tolower(StyleAndType), "three")) &
        str_detect(tolower(StyleAndType), "4") == TRUE ~ "Both or Multiple",
      str_detect(tolower(StyleAndType), "3 row") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "3-row") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "3row") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "three") == TRUE ~ "3 row",
      str_detect(tolower(StyleAndType), "4 row") == TRUE ~ "4 row",
      str_detect(tolower(StyleAndType), "4-row") == TRUE ~ "4 row",
      TRUE ~ "Not specified"
    )
  ) %>%
  filter(Type != "Not specified") %>%
  count(SurveyType, Type)
```

A total of `r instrument_type %>% filter(Type == "3 row") %>% summarise(t = sum(n)) %>% pull(t)`, or `r percent(instrument_type %>% filter(Type == "3 row") %>% summarise(t = sum(n)) %>% pull(t)/ instrument_type %>% summarise(t = sum(n)) %>% pull(t))` of respondents are working with a 3-row nyckelharpa, and we did find a difference in ANA members and non-members, with more members having 4-row and multiple types of harpas than respondents who were not members.

```{r instrument_plot}
ggplot(instrument_type, aes(y = n, x = SurveyType)) +
  geom_bar(position = "fill", stat = "identity", 
           aes(fill = Type)) +
  scale_fill_viridis(discrete = TRUE, alpha = .8) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "", y = "") +
  scale_y_continuous(labels = scales::percent)


```

## Experience 

```{r}
experience <- rbind(general %>%
                      select(Experience, SurveyType),
                    member %>% select(Experience, SurveyType)) %>%
  mutate(
    ExperienceAdjust = case_when(
      str_detect(Experience, "5 years,") |
        str_detect(Experience, "15") |
        str_detect(Experience, "Leif") ~ "More than 5 years",
      str_detect(Experience, "Never") |
        str_detect(Experience, "awhile") |
        str_detect(Experience, "priority") ~ "I don't play (yet)",
      str_detect(Experience, "4 years") ~ "2-5 years",
      TRUE ~ Experience
    ),
    ExperienceAdjust = factor(ExperienceAdjust,
                              levels = c(
                                "I don't play (yet)",
                                "0-2 years",
                                "2-5 years",
                                "More than 5 years"
                              ))
  )

experience %>%
  count(ExperienceAdjust, SurveyType) %>%
  ggplot(aes(x = SurveyType, y = n, fill = ExperienceAdjust)) +
  geom_bar(stat = "identity", alpha = .8) +
  scale_fill_viridis("", discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "", y = "", title = "Experience") 
```


## Music 

### Styles

Top 5 most used words of interest in regard to style of playing across both the member and general surveys.

```{r styles}

styles <- interests %>%
  select(StyleAndType) %>%
  mutate(StyleAndType = str_replace(StyleAndType, "/", " ")) %>%
  separate(
    StyleAndType,
    into = c(letters, LETTERS, 
             paste0(letters, "a"), 
             paste0(LETTERS, "a")),
    fill = "right",
    sep = " "
  ) %>%
  pivot_longer(cols = everything(),
               names_to = "deletethis") %>%
  select(-deletethis) %>%
  mutate(
    value = tolower(value),
    value = str_replace_all(tolower(value), "traditional", "trad"),
    value = str_replace_all(value, "trad", "traditional"),
    value = gsub("[[:punct:][:blank:]]+", " ", value),
    value = str_trim(value, side = "both"),
    CharLength = nchar(value)
  ) %>%
  filter(CharLength > 3 &
           str_detect(value, "3") == FALSE &
           str_detect(value, "4") == FALSE &
           !value %in% c("also", "mostly", "tuned", "like", "from",
                         "play", "music", "tunes", "tuning",
                         "nyckelharpa", "repertoire", "chromatic",
                         "standard", "fiddle")) %>%
  count(value) %>%
  arrange(desc(n)) %>%
  head(5) %>%
  rename("Word" = value, "Frequency" = n) %>%
  mutate(Word = str_to_title(Word))

style_count <- interests %>%
  select(StyleAndType) %>%
  filter(!is.na(StyleAndType)) %>%
  nrow()

styles %>%
  mutate(Word = fct_reorder(Word, desc(Frequency))) %>%
  ggplot(aes(x = Word, y = Frequency, fill = Word)) +
  geom_col(alpha = .8) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Styles",
    caption = paste(style_count,
                     "respondents used these words most often"),
    x = "",
    y = ""
  ) +
  geom_hline(aes(yintercept = style_count + 2)) +
  scale_fill_viridis(discrete = TRUE) +
  geom_label(
    label = paste(style_count, "respondents"),
    x = 4.1,
    y = style_count + 1,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  theme(axis.text.x = 
          element_text(angle = 33, vjust = 0.5, hjust = 1)) + 
  guides(fill = "none") 

```

#### Interest in Swedish and Uppland

On a scale from 0 to 2, the average interest levels in the two traditions represented in the survey are:
```{r}

average_interest_swedish <- 
  mean(c(interests$InterestInSwedish), na.rm = TRUE) 
  
average_interest_uppland <- 
  mean(c(interests$InterestInUppland), na.rm = TRUE)

interest_national <- data.frame(Type = c("Swedish", "Uppland"),
                            AverageInterest = c(
                              average_interest_swedish,
                              average_interest_uppland
                            ),
                            Denominator = 2)

interest_national %>%
  ggplot(aes(x = Type, fill = Type)) +
  geom_segment(aes(xend = Type, y = 0, yend = AverageInterest),
               color = "dark gray") +
  geom_point(aes(y = AverageInterest),
             fill = "blue",
             size = 4, 
             alpha = .7,
             shape = 21) +
  geom_hline(yintercept = 2) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Interest in Swedish and Uppland Styles",
    x = "",
    y = "Average Interest"
  ) +
  geom_label(
    label = "Strong Interest ->",
    x = 2.5,
    y = 1.75,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
    geom_label(
    label = "<- No Interest",
    x = 2.5,
    y = .2,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() +
  guides(fill = "none")


```

### Tunes

#### Favorites

```{r}

too_many <- interests %>%
  select(Faves) %>%
  mutate(
    TooMany =
      case_when(
        Faves == "N/A" | is.na(Faves) ~ "No response",
        str_detect(tolower(Faves),
                   "too many",
                   negate = TRUE) == FALSE &
          str_detect(Faves, "That is a very hard question",
                     negate = FALSE) == FALSE ~ "TRUE",
        TRUE ~ "FALSE"
      )
  ) %>%
  count(TooMany)

```

Of the `r too_many %>% filter(TooMany == "FALSE") %>% pull(n) + too_many %>% filter(TooMany == "TRUE") %>% pull(n)` who answered the question about their 3 favorite tunes, `r too_many %>% filter(TooMany == "TRUE") %>% pull(n)` protested that the question was too difficult given how many great tunes there are. Of those who included tune names in their response, here are some tunes named more than once.

```{r}

tunes <- interests %>%
  select(Faves) %>%
  mutate(
    TooMany =
      case_when(
        Faves == "N/A" | is.na(Faves) ~ "No response",
        str_detect(tolower(Faves),
                   "too many",
                   negate = TRUE) == FALSE &
          str_detect(Faves, "That is a very hard question",
                     negate = FALSE) == FALSE ~ "TRUE",
        TRUE ~ "FALSE"
      ),
    Faves = str_replace_all(Faves, ";", ","),
    Faves = str_replace(tolower(Faves), "currently ", ""),
    Faves = str_replace_all(tolower(Faves),
                            "spelmansgladje",
                            "spelmansglädje"),
    Faves = case_when(
      Faves ==
        "zakaria jansons polska / gånglåt från laggars / polska efter andersson" ~
        "zakaria jansons polska, gånglåt från laggars, polska efter andersson",
      str_detect(tolower(Faves), "i suppose something") ~
        "ipa gubban, josefine's waltz",
      tolower(Faves) == "båtsman däck  -boda waltz   timeless waltz" ~
        "båtsman däck, boda waltz, timeless waltz",
      str_starts(tolower(Faves), "stures") ~
        "stures schottis, halleforsnaspolska",
      TRUE ~ Faves
    ), 
    Faves = str_replace(tolower(Faves),
                        "that is a very hard question. ", "")
  ) %>%
  filter(TooMany == "FALSE") %>%
  select(-TooMany) %>%
  separate(Faves,
           into = c(letters),
           sep = ", ",
           fill = "right") %>%
  pivot_longer(cols = everything()) %>%
  filter(!is.na(value)) %>%
  mutate(
    value = str_trim(value),
    value = tolower(value),
    value = str_remove_all(value, "and "),
    value = str_remove_all(value, "also "),
    value = case_when(
      str_starts(value, "at the moment") ~ "spelmansglädje",
      value == "bygnan" ~ "byggnan",
      str_starts(value, "hard to narrow") |
        value == "harjedals schottis" ~ "härjedalsschottis",
      str_starts(value, "hom") ~ "hommage till en spelman",
      str_starts(value, "jose") |
        str_starts(value, "tough") ~ "josephine's dopvals",
      str_starts(value, "karol") ~ "karolinersmarch",
      str_starts(value, "most any tune") ~ "eklundspolska #3",
      str_starts(value, "sheesh") ~ "spelmansglädje",
      str_starts(value, "so i'll") ~ "trollrikepolskan",
      str_starts(value, "spelglädjen") ~ "spelmansglädje",
      str_starts(tolower(value), "spelmans") ~ "spelmansglädje",
      str_detect(tolower(value), "ali’s waltz") ~ "ali's waltz",
      str_starts(value, "vendelpolskan") ~ "vendelpolskan",
      TRUE ~ value
    )
  ) %>% 
  filter(str_detect(value, "lots of others", negate = TRUE),
         str_detect(value, "american question", negate = TRUE),
         str_detect(value, "but i really", negate = TRUE),
         str_detect(value, "dalarna the adjoining areas", negate = TRUE),
         str_detect(value, "i could not possibly", negate = TRUE),
         str_starts(value, "many sahlstrom", negate = TRUE),
         str_starts(value, "not sure", negate = TRUE),
         value != "oh",
         str_starts(value, "really liked", negate = TRUE),
         str_starts(value, "since that", negate = TRUE),
         str_starts(value, "so not possible", negate = TRUE),
         str_starts(value, "these vary", negate = TRUE),
         str_starts(value, "this is", negate = TRUE),
         str_detect(value, "pretty exclusively", negate = TRUE),
         str_starts(value, "too diff", negate = TRUE),
         str_starts(value, "tunes", negate = TRUE),
         str_starts(value, "wow", negate = TRUE),
         str_starts(value, "varies", negate = TRUE)
         ) %>%
  count("Tune" = value) %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>%
  mutate(Tune = str_to_title(Tune)) %>%
  rename("Mentions" = n)

gt(tunes) %>%
  tab_options(table.font.size = px(22))
	
```

#### Allspel Suggestions

```{r}

allspiel <- rbind(
  general %>%
    select(AllspielSuggestions,
           SurveyType),
  member %>%
    select(AllspielSuggestions,
           SurveyType)
) 

allspiel_responses <- allspiel %>% filter(!is.na(AllspielSuggestions))

allspiel_respondents <- 
  allspiel_responses  %>% nrow()

```

From `r allspiel_respondents` responses to the survey question asking for tune suggestions to add to the [Allspel list](http://www.nyckelharpa.org/archive/written-music/american-allspel-list/), the following tunes were noted:

  * 1814
  * Adventspolskan
  * Bisonpolska
  * Eklundapolska 1 & 3
  * Elins Vals
  * Femtolen
  * Flickorna Svensson
  * Hambo efter Carl Johan Krej
  * Hommage til en Spelman
  * Härjedalsschottis
  * Juringius
  * Karl XII Vals
  * Kyrkpolska
  * Langdans fran Solleron
  * Polska efter Hugo Falk
  * Ridmarsch efter Byss-Calle
  * Schottis fr. Härjedalen
  * Spelmansglädje
  * Stures 80-år schottis
  * Älvdalensbrudmarsch
  * Äppelbo Gånglåt
  * Österbypolska

## Feedback {.tabset .tabset-pills}

### Website 

#### Website Traffic

```{r}

website <- rbind(
  general %>%
    select(SiteVisits,
           SitePurpose,
           SiteSuggestions,
           SurveyType),
  member %>%
    select(SiteVisits,
           SitePurpose,
           SiteSuggestions,
           SurveyType)
) %>% 
  unique()

how_often <- website %>%
  group_by(SurveyType) %>%
  summarise(VisitAvg = mean(SiteVisits, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Denominator = 2)

how_often %>%
  ggplot(aes(x = SurveyType, fill = SurveyType)) +
  geom_segment(aes(xend = SurveyType, y = 0, yend = VisitAvg),
               color = "dark gray") +
  geom_point(aes(y = VisitAvg),
             fill = "blue",
             size = 4, 
             alpha = .7,
             shape = 21) +
  geom_hline(yintercept = 2) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Website Visits",
    x = "",
    y = "How Often"
  ) +
  geom_label(
    label = "Often ->",
    x = 2.5,
    y = 1.85,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
    geom_label(
    label = "<- Never",
    x = 2.5,
    y = .15,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() +
  guides(fill = "none")

```

#### Why do people come to the website? 

There was no significant difference between responses from members vs non-members, except fewer members are looking to buy a nyckelharpa. Taking all the answers together, including respondents selecting multiple selections, here are the reasons people are coming to the website:
<br>
<br>
```{r}
site_purpose <- website %>%
  select(SitePurpose) %>%
  separate(
    SitePurpose,
    sep = ", ",
    into = c("a", "b", "c", "d", "e", "f", "g", "h"),
    fill = "right"
  ) %>%
  pivot_longer(cols = all_of(1:8)) %>%
  filter(!is.na(value)) %>%
  count(value) %>%
  filter(n > 1) %>%
  arrange(desc(n)) %>%
  rename("Reasons" = value, "Clicks" = n) %>%
  mutate(Reasons = case_when(
    str_detect(Reasons, "events") ~ "Nyckelharpa events",
    str_detect(Reasons, "maintenance") ~ "Nyckelharpa maintenance",
    str_detect(Reasons, "music") ~ "Nyckelharpa music",
    str_detect(Reasons, "instrument") ~ "Nyckelharpa & its history",
    str_detect(Reasons, "buy") ~ "How to buy a nyckelharpa"
  ))

site_purpose_count <- website %>%
  select(SitePurpose) %>%
  filter(!is.na(SitePurpose)) %>%
  nrow()

site_purpose %>%
  mutate(Reasons = fct_reorder(Reasons, Clicks)) %>%
  ggplot(aes(x = Reasons, y = Clicks, fill = Reasons)) +
  geom_col(alpha = .8) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Site Purpose",
    caption = 
      paste(site_purpose_count,
            "respondents selected the reasons they come to the site"), 
    x = "",
    y = ""
  ) +
  ylim(0, 75) +
  geom_hline(aes(yintercept = site_purpose_count)) +
  scale_fill_viridis(discrete = TRUE) +
  geom_label(
    label = paste(site_purpose_count, "respondents"),
    x = 4.1,
    y = site_purpose_count,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() + 
  guides(fill = "none")

```
<br>
In the space for additional comments, several respondents mentioned that they used to visit the website many years ago but not much recently. Other respondents mentioned that they come to the website for the member directory, to find nyckelharpa players in their area. **We no longer publish a player directory, but people can write to [info@nyckelharpa.org](mailto:info@nyckelharpa.org) to ask about players in their area!**

<br>

### Virtual Jam

```{r}

jams <- rbind(
  general %>%
    select(VirtualJamInterest,
           VirtualJamInterest,
           SecondSaturday,
           JamFacilitatorInterest,
           Nov13JamFeedback,
           SurveyType),
  member %>%
    select(VirtualJamInterest,
           VirtualJamInterest,
           SecondSaturday,
           JamFacilitatorInterest,
           Nov13JamFeedback,
           SurveyType)
) 

jam_interest_respondents <- 
  jams %>% 
  filter(!is.na(JamFacilitatorInterest)) %>% 
  nrow()

jam_interest <- mean(c(jams$VirtualJamInterest), na.rm = TRUE)

jam_facilitator_definitely <-
  jams %>% 
  count(JamFacilitatorInterest) %>% 
  filter(JamFacilitatorInterest == 2) %>% 
  pull(n)

jam_facilitator_maybe <- 
  jams %>% 
  count(JamFacilitatorInterest) %>% 
  filter(JamFacilitatorInterest == 1) %>% 
  pull(n)

```

`r as.english(jam_interest_respondents)` responded to the question gauging interest (0 to 2) in a virtual Zoom jam, where 0 is no interest and 2 is a strong interest.


```{r}
jam_interest_by_member_type <- jams %>%
  group_by(SurveyType) %>%
  summarise(
    Interest = mean(VirtualJamInterest, na.rm = TRUE)
  ) %>%
  ungroup()

jam_interest_by_member_type %>%
  ggplot(aes(x = SurveyType, fill = SurveyType)) +
  geom_segment(aes(xend = SurveyType, 
                   y = 0, 
                   yend = Interest),
               color = "dark gray") +
  geom_point(aes(y = Interest),
             fill = "blue",
             size = 4, 
             alpha = .7,
             shape = 21) +
  geom_hline(yintercept = 2) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Interest in a Virtual Jam",
    x = "",
    y = "Average Interest"
  ) +
  geom_label(
    label = "Strong Interest ->",
    x = 2.5,
    y = 1.75,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
    geom_label(
    label = "<- No Interest",
    x = 2.5,
    y = .2,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() +
  guides(fill = "none")

```

Comparing interest between members and non-members, most members had a strong interest, whereas non-members were more divided, but most were at least somewhat interested in a virtual jam.

Encouragingly, there was `r jam_facilitator_definitely` respondent very interested in facilitating, and `r jam_facilitator_maybe` respondents somewhat interested in facilitating a jam.

The ANA appreciates all the feedback regarding the current time slot for virtual jams and for the feedback regarding the Zoom jam held November 13, 2021.  

### Virtual Workshop 

```{r}
workshop <- rbind(
  general %>%
    select(starts_with("VirtualWorkshop"),
           SurveyType),
  member %>%
    select(starts_with("VirtualWorkshop"),
           SurveyType)
)

workshop_interest <- workshop %>%
  group_by(SurveyType) %>%
  summarise(interest = 
              mean(c(workshop$VirtualWorkshopInterest),
                   na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Denominator = 2)

```

#### Overall Interest

Overall interest in virtual workshops on a scale from 0 (no interest) to 2 (strong interest) came out *exactly even* between members and non-members at an average of `r format(workshop_interest$interest[1], digits = 3)`.

```{r}

workshop_interest %>%
  ggplot(aes(x = SurveyType, fill = SurveyType)) +
  geom_segment(aes(xend = SurveyType, 
                   y = 0, 
                   yend = interest),
               color = "dark gray") +
  geom_point(aes(y = interest),
             fill = "blue",
             size = 4, 
             alpha = .7,
             shape = 21) +
  geom_hline(yintercept = 2) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Interest in a Virtual Workshop",
    x = "",
    y = "Average Interest"
  ) +
  geom_label(
    label = "Strong Interest ->",
    x = 2.5,
    y = 1.75,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
    geom_label(
    label = "<- No Interest",
    x = 2.5,
    y = .2,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) +
  coord_flip() +
  guides(fill = "none")

```

#### Workshop Topics

```{r}

tunes <- "Learning tunes"
tune_types <- "particular tune types"
dancing <- "Playing for dancing"
maintenance <- "Maintenance for your nyckelharpa"
beginners <- "Getting started with the nyckelharpa for beginners"
harmonies <- "Playing harmonies"

workshop_types <- workshop %>%
  select(VirtualWorkshopTypes) %>%
  filter(!is.na(VirtualWorkshopTypes)) %>%
  mutate(
    Tunes = if_else(str_detect(VirtualWorkshopTypes, tunes), 1, 0),
    TuneTypes = if_else(str_detect(VirtualWorkshopTypes, tune_types), 1, 0),
    Dancing = if_else(str_detect(VirtualWorkshopTypes, dancing), 1, 0),
    Maintenance = if_else(str_detect(VirtualWorkshopTypes, maintenance), 1, 0),
    Beginners = if_else(str_detect(VirtualWorkshopTypes, beginners), 1, 0),
    Harmonies = if_else(str_detect(VirtualWorkshopTypes, harmonies), 1, 0),
    Other = case_when(
      str_detect(VirtualWorkshopTypes, tunes, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, harmonies, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, tune_types, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, dancing, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, maintenance, negate = TRUE) &
        str_detect(VirtualWorkshopTypes, beginners, negate = TRUE) ~ 
        VirtualWorkshopTypes
    )
  ) %>%
  select(-VirtualWorkshopTypes, -Other) %>%
  map_dbl(., sum) %>%
  bind_rows() %>%
  pivot_longer(cols = everything(),
               names_to = "Topics") %>%
  arrange(desc(value))

workshop_type_count <- workshop %>%
  select(VirtualWorkshopTypes) %>%
  filter(!is.na(VirtualWorkshopTypes)) %>%
  nrow()

workshop_types %>%
  mutate(Topics = case_when(
           Topics == "Dancing" ~ "Playing for Dancing",
           Topics == "Maintenance" ~ "Nyckelharpa Maintenance",
           Topics == "TuneTypes" ~ "Tune types",
           Topics == "Tunes" ~ "Learning tunes",
           TRUE ~ Topics
         ),
         Topics = fct_reorder(Topics, desc(value))) %>%
  ggplot(aes(x = Topics, y = value, fill = Topics)) +
  geom_col(alpha = .8) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(
    title = "Workshop Topics of Interest",
    caption = paste(workshop_type_count,
                     "respondents selected multiple topics"),
    x = "",
    y = ""
  ) +
  geom_hline(aes(yintercept = workshop_type_count + 2)) +
  scale_fill_viridis(discrete = TRUE) +
  geom_label(
    label = paste(workshop_type_count, "\nrespondents"),
    x = 4.1,
    y = workshop_type_count - 4,
    label.padding = unit(0.25, "lines"),
    label.size = 0.25,
    color = "black",
    fill = "#5DC863FF"
  ) + 
  coord_flip() +
  guides(fill = "none")

```
<br>


### Newsletter

```{r}

newsletter <- rbind(
  general %>%
    select(starts_with("Newsletter"),
           SurveyType),
  member %>%
    select(starts_with("Newsletter"),
           SurveyType)
)

newsletter_interest <- newsletter %>%
  rowid_to_column() %>%
  mutate( # had to assign responses into buckets manually
    Receiving = case_when(
      rowid %in% c(1:3, 5:8, 10:11, 13:20, 22:24, 27, 29:32, 34:37, 40:45, 50:53, 57:67, 69:72, 75:79) ~ "Yes",
      rowid %in% c(25:26, 28, 33, 39, 46, 54:56, 68, 73) ~ "No",
      TRUE ~ "Did not answer"),
    Contributing = case_when(
      rowid %in% c(2, 11, 14, 16, 19, 27, 35, 43, 59, 61, 62, 66, 67, 68, 69, 71, 77, 79) ~ "Yes",
      rowid %in% c(45, 13, 41, 63, 32, 34, 57, 3, 28, 37, 78, 70, 21, 33) ~ "No",
      TRUE ~ "Did not answer")
    )

newsletter_interest_receiving <- newsletter_interest %>%
  count(SurveyType, Receiving)

newsletter_interest_contributor <- newsletter_interest %>%
  count(SurveyType, Contributing)

newsletter_receiving <- newsletter_interest %>%
  count(Receiving) %>%
  adorn_percentages(denominator = "col") %>%
  adorn_pct_formatting(digits = 0)
```

`r newsletter_receiving %>% filter(Receiving == "Yes") %>% pull(n)` of all respondents indicated an interest in receiving a regular ANA newsletter.

```{r}

newsletter_interest_receiving %>%
  ggplot(aes(x = SurveyType, y = n, fill = Receiving)) +
  geom_bar(stat = "identity", alpha = .8) +
  scale_fill_viridis("", discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "", y = "", title = "Interest in Reading ANA Newsletter") 

```

It was encouraging that there were `r sum(newsletter_interest_contributor %>% filter(Contributing == "Yes") %>% pull(n))` respondents who were interested in contributing content, layout and design services, and/or money toward its creation.

```{r}

newsletter_interest_contributor %>%
  ggplot(aes(x = SurveyType, y = n, fill = Contributing)) +
  geom_bar(stat = "identity", alpha = .8) +
  scale_fill_viridis("", discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "", y = "", title = "Interest in Contributing to an ANA Newsletter") 

```


### Membership 

#### Membership Interest (from non-members)

```{r}

membership <- rbind(
  general %>%
    select(starts_with("Membership"),
           VolunteerInterest,
           SurveyType),
  member %>%
    select(starts_with("Membership"),
           VolunteerInterest,
           SurveyType) %>%
    mutate(MembershipInterest = "Already a member")
)

membership_interest_count <- membership %>%
  filter(!is.na(MembershipInterest) &
           MembershipInterest != "Already a member") %>% nrow()

membership_benefits_count <- membership %>%
  filter(!is.na(MembershipBenefits)) %>% nrow()

volunteer_interest <- membership %>%
  select(VolunteerInterest, SurveyType) %>%
  rownames_to_column() %>%
  mutate(
    Volunteer = case_when(
      is.na(VolunteerInterest) ~ "No answer",
      rowname %in% c(49, 14, 33) ~ "No",
      TRUE ~ "Yes"))

board_interest <- member %>%
  select(FreeStyle) %>%
  rownames_to_column() %>%
  mutate(
    BoardVolunteer = case_when(
      is.na(FreeStyle) ~ "No answer",
      rowname %in% c(6, 8, 17) ~ "Maybe",
      TRUE ~ FreeStyle
    )
  )

membership_interest <- membership %>%
  filter(!is.na(MembershipInterest) & 
           MembershipInterest != "Already a member") %>%
  mutate(
    MembershipInterest = case_when(
      MembershipInterest %in% c("Yes", "Just signed up.") ~ "Yes",
      MembershipInterest == "No" ~ "No",
      TRUE ~ "Maybe"
    ),
    MembershipInterest = factor(MembershipInterest,
                                levels = c("Yes", "Maybe", "No"))
  ) %>% 
  count(MembershipInterest) 

```

Of the `r membership_interest_count` non-member respondents who answered this question, there was strong interest in [ANA membership](http://www.nyckelharpa.org/about/about-the-ana/become-a-member/). 

```{r}

ggplot(membership_interest, 
       aes(x = MembershipInterest, y = n, fill = MembershipInterest)) +
  geom_col(alpha = .8) +
  scale_fill_viridis(discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  guides(fill = "none") +
  labs(
    title = "Interest in Membership (from non-members)",
    x = "",
    y = ""
  )

```


#### Membership Benefits

```{r}
benefits <- tribble(
  ~Benefits, ~Count,
  "discounts",	4,
  "finding others",	6,
  "access",	7,
  "na",	11,
  "none",	19
)
```

The question about membership benefits was interpreted broadly by the respondents who answered it. Here are some key takeaways:

  * Most felt like adding benefits to ANA membership was unnecessary
  * Others associated membership benefits with finding other players, access to content, information about events, and a few people mentioned discounts
  * Community and keeping the nyckelharpa alive was a common theme

### Volunteering

#### Volunteering Generally

This question was asked of both members and non-members. Respondents who checked one or more of the options are counted as "Yes". The options given were:

  * Newsletter design
  * Newsletter content
  * Website content
  * Making videos to share on the website
  * Surveys
  * Media (collecting photos)
  * Assisting at virtual jams
  * Assisting at virtual workshops
  * Social media

```{r}

volunteer_interest %>%
  ggplot(aes(x = SurveyType, fill = Volunteer)) +
  geom_bar(alpha = .8) +
  scale_fill_viridis("", discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "", y = "", title = "Interest in Volunteering")

```

#### Board Volunteer (Member Survey Only)

This question was only on the member survey. Any respondents that did not answer with a direct Yes/No/Maybe were counted as "Maybe."

```{r}

board_interest %>%
  ggplot(aes(BoardVolunteer, fill = BoardVolunteer)) +
  geom_bar(alpha = .8) +
  scale_fill_viridis("Board\nVolunteer", discrete = TRUE) +
  theme_minimal() +
  theme(text = element_text(size = 18)) +
  labs(x = "", y = "", title = "Interest in Serving on the ANA Board")

```


### Survey 

```{r}
survey_feedback <- rbind(
  general %>%
    select(SurveyFeedback,
           SurveyType),
  member %>%
    select(SurveyFeedback,
           SurveyType)
)

survey_feedback_count <- survey_feedback %>%
  filter(!is.na(SurveyFeedback)) %>% nrow()

```

Thank you to the `r str_to_sentence(as.english(survey_feedback_count))` respondents who gave feedback on the survey itself. We will do our best to incorporate your suggestions into future surveys.

## {-}

# {-}

---

So much thanks to everyone who participated in the analysis! Be sure to click through the tabs above. The R code used to produce this analysis can be found on [GitHub](https://github.com/kiadso/nyck-survey).

Please send feedback any time to [nyckelnotes@nyckelharpa.org](mailto:nyckelnotes@nyckelharpa.org). 


